Make manuscript figures

### 2022-06-11 scripts/R/make_manuscript_figures.rmd
fix dimensions of simulation example fig

# Plot trait values on a clade in the tree
mar <- 20
lo_h2_tree <- ggtree(single_clade) %<+% example_data_lo_h2 + 
        geom_tippoint(aes(color = v), size = 3) + 
        scale_color_viridis_b(name = "Pathogen\npart of trait") + 
        theme_tree(plot.margin=margin(mar, mar, mar, mar))

hi_h2_tree <- ggtree(single_clade) %<+% example_data_hi_h2 + 
        geom_tippoint(aes(color = v), size = 3) + 
        scale_color_viridis_b(name = "Pathogen\npart of trait") + 
        theme_tree(plot.margin=margin(mar, mar, mar, mar))

# Plot trait value accuracy
p1 <- ggplot(data = example_data, aes(x = h, y = h.MWA)) +
      geom_point() +
      facet_grid(. ~ Heritability, labeller = "label_both") + 
      shared_theme +
      labs(x = "Simulated host part of trait", y = ehat_name)

# Arrange plots together
top_row <- plot_grid(
        lo_h2_tree + theme(legend.position = "none"),
        hi_h2_tree + theme(legend.position = "none"),
        labels = c("A", "B"),
        nrow = 1
)
plot_grid(top_row, get_legend(lo_h2_tree),
          p1,
          nrow = 2, align = "v", axis = "tb",
          rel_heights = c(1, 1.5),
          rel_widths = c(1, 0.2),
          labels = c("", "", "C"))
ggsave(filename = paste(FIGDIR, "example_simulation_trait_values.png", sep = "/"),
      width = linewidth, height = height * 1.3, unit = "cm")
```

>>>>

# Plot trait values on a clade in the tree
mar <- 20
lo_h2_tree <- ggtree(single_clade) %<+% example_data_lo_h2 + 
        geom_tippoint(aes(color = v), size = 3) + 
        scale_color_viridis_b(name = "Pathogen\npart of trait") + 
        theme_tree(plot.margin=margin(0, mar, 0, mar))

hi_h2_tree <- ggtree(single_clade) %<+% example_data_hi_h2 + 
        geom_tippoint(aes(color = v), size = 3) + 
        scale_color_viridis_b(name = "Pathogen\npart of trait") + 
        theme_tree(plot.margin=margin(0, mar, 0, mar))

# Plot trait value accuracy
p1 <- ggplot(data = example_data, aes(x = h, y = h.MWA)) +
      geom_point() +
      facet_grid(. ~ Heritability, labeller = "label_both") + 
      shared_theme +
      labs(x = "Simulated host part of trait", y = "Estimated non-pathogen\npart of trait")

# Arrange plots together
top_row <- plot_grid(
        lo_h2_tree + theme(legend.position = "none"),
        hi_h2_tree + theme(legend.position = "none"),
        labels = c("A", "B"),
        nrow = 1
)
plot_grid(top_row, get_legend(lo_h2_tree),
          p1,
          nrow = 2, align = "v", axis = "tb",
          rel_heights = c(1, 1.5),
          rel_widths = c(1, 0.2),
          labels = c("", "", "C"))
ggsave(filename = paste(FIGDIR, "example_simulation_trait_values.png", sep = "/"),
      width = linewidth, height = height, unit = "cm")
```
